\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Manas}{Gupta}{\href{https://manas11.github.io/}{https://manas11.github.io/}\\
\href{mailto:manasgupta1109@gmail.com}{manasgupta1109@gmail.com} | +918818884950
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{NITK, SURATHKAL}
\descript{B.Tech. in Computer Science and Engineering}
\location{CGPA: 8.13}
\sectionsep

\subsection{Sacred Heart Co-Ed Sr.Sec. School, Indore}
\descript{Class XII (CBSE) | 94.4\%}
\sectionsep
\descript{Class X (CBSE) | CGPA: 10.00}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
GitHub:// \href{https://github.com/manas11}{\custombold{manas11}} \\
LinkedIn://  \href{https://www.linkedin.com/in/manasgupta11}{\custombold{manasgupta11}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Data Structures and Algorithms \\
Object Oriented Programming \\
Software Engineering \\
Operating Systems \\
Computer Organization and Architecture \\
Concrete Mathematics \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements} 
AIR 2770 in JEE Mains out of 1.2 million candidates.\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{IRIS NITK}
\descript{| Backend Developer Intern}
\location{May 2019 – July 2019}
\vspace{\topsep}
\begin{tightemize}
\item We are a team of motivated students from NITK Surathkal, developing and expanding a digital portal that ensures that all administrative, academic and alumni related procedures take place methodically.\item Worked on developing the Employees Complaints Module to manage complaints filed by the employees at NITK. This module is used by about 500 employees.\item Made enhancements to the Employee Quarters Module. Added manual allocation, de-allocation of quarters, and option to import initial data from CSV.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Bargainer Android Application}
\begin{tightemize}
\item Developed an Android Application to help those people who do not have bargaining skills and can easily be conned or for those people who have moved to a new town and have less knowledge about the shops.
\item Implemented location-based search using Google Places API, end to end chat, QRCode based payment, and integrated the application with Firebase Database.
\end{tightemize}
\sectionsep

\runsubsection{DSL and Automated Code Generation}
\begin{tightemize}
\item Developed a DSL(Domain Specific Language) and generated automated code segments to reduce energy-related code smells in Android applications.\item Used Xtext for DSL and Xtend for code generation. Deployed as an Eclipse plugin to be used by the android developers.
\end{tightemize}
\sectionsep

\runsubsection{\href{https://github.com/manas11/ns-3-dce-assignment}{Iperf In ns-3 DCE}}
\begin{tightemize}
\item Worked on adding dumbbell topology with n clients, two routers, one server in ns-3 DCE(Direct Code Execution).\item Used Iperf client on the server and clients to measure bandwidth and latency with a change in the TCP window size, number of clients, and UDP usage.   
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Acquainted:}
C \textbullet{}   C++ \textbullet{} Java    \textbullet{} Android Studio  \textbullet{} Ruby on Rails \textbullet{ }HTML5\\
\location{Familiar:}
Python \textbullet{} MySQL \textbullet{}  LaTex\textbullet{} Git \textbullet{} Xtext
\sectionsep


\end{minipage} 
\end{document}